---
title: "chapter5-plot"
output: html_notebook
---
고수준 그래프함수
- plot
- xyplot
- boxplot
- hist
- curve
- coplot

```{r}
data(mtcars)

plot(mtcars) #pairs()
plot(mtcars$mpg) 
plot(mpg ~ disp, data=mtcars) #xyplot()
plot(mpg ~ factor(am), data=mtcars) #boxplot()
coplot(mpg ~ disp | factor(am), data=mtcars) #3개의 변수 관계

methods(plot) #plot 의 다형성 보기
```

제목
- main
- xlab, ylab

축설정
- xlim, ylim

모양, 색설정
- type(p, l, b, c, n 등)
- pch(점 모양)
- cex(점 크기)
- col(점 테두리 색)
- bg(점 내부 색)

저수준 그래픽 함수 추가
- 제목 : title()
- 범례 : legend(location, legend), mtext()
- 축 : axis(side(축 위치)=, at=, labels=, line=)
- 점 : points(x, y, pch(점 모양)=, cex(점 크기)= )
- 선 : lines(x, y, lty(전 종류)=, lwd=, col=)
      abline(a, b) y=a+b*x 인  선
      grid(nx(가로줄 수)=, ny(세로줄 수)= )
      segments()
- 텍스트 : text(x, y, labels= , cex=, pos(상하좌우)= )
          mtext()
- 도형 : polygon()
- 수학식 : expression() --> demo(plotmath)를 참고

저장
- jpeg(), pdf()

화면분할
- mfrow(), layout()


```{r}
par(mfrow=c(2,2))
plot(1:10, main="default(type=\"p\")") #점
plot(1:10, type="l", main="default(type=\"l\")") #선 
plot(1:10, type="b", main="default(type=\"b\")") #둘다
plot(1:10, type="n", main="default(type=\"n\")") #빈칸
par(mfrow=c(1,1))
```

```{r}
#그래프의 중첩
#1 add=TRUE
plot(sin, -pi, pi, ylab="y")
plot(cos, -pi, pi, add=TRUE, lty="dotted", col="red")
legend(0, -0.5, legend=c("sin","cos"), lty=1:2, col=1:2)

#2 par(new=TRUE)
F= function(x,a) {1/(1+exp(-a-x))}
curve(F(x,-1), col=1, xlim=c(-5,5), ylim=c(0,1), ylab="f(x)")
par(new=TRUE)
curve(F(x,1), col=2, xlim=c(-5,5), ylim=c(0,1), ylab="", axes=FALSE, lty=2)
title(main=expression(f(x)==frac(1, 1+exp(-a-x))))


```


```{r}
#저장
help(Devices)
png(filename="myplot1.png", width=480, height=480, units="px")
plot(mpg~disp, data=mtcars)
dev.off()
```

```{r}
#그림 배열의 미세 조절
#fig를 사용
opar <- par(no.readonly = T)
par(fig = c(0, 0.8, 0, 0.8))
plot(mtcars$wt, mtcars$mpg, xlab = "miles per gallon", ylab="car weight")
par(fig = c(0, 0.8, 0.55, 1), new=TRUE)
boxplot(mtcars$wt, horizontal=TRUE, axes=FALSE)
par(fig = c(0.65, 1, 0, 0.8), new=TRUE)
boxplot(mtcars$mpg, axes=FALSE)
mtext("enhanced scatterplot", side=3, outer=TRUE, line=-3)
par(opar)
```


```{r histogram}
hist(acs$BMI)
hist(acs$BMI, breaks=20, col="red", 
     main="Distribution", xlab=expression(BMI(kg/m^2)))

hist(acs$BMI, breaks=20, col="red", freq=FALSE, 
     main="Distribution", xlab=expression(BMI(kg/m^2)))
rug(acs$BMI)
lines(density(acs$BMI, na.rm=TRUE), col="blue", lwd=2)
```

```{r Kernel density plots}
par(mfrow = c(2,1))
d=density(acs$BMI, na.rm=T)
plot(d)
plot(d, main="Kernel Density of BMI")
polygon(d, col="red", border = "blue", lwd=2)
rug(acs$BMI, col="black")
par(mfrow=c(1,1))

dm=density(acs$weight[acs$sex=="Male"], na.rm=T)
df=density(acs$weight[acs$sex=="Female"], na.rm=T)
plot(df, col="blue", lty=1)
lines(dm, col="red", lty=2)
legend("topright", legend=c("Male", "Female"), col=c("red", "blue"), lty=c(2,1))
```


```{r boxplot}
boxplot(acs$BMI, col="red")
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
